Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-09-29 main.tex
Started on algorithm tikz picture, that captures the 3 algorithm steps Fixed missing weights x_ky_k in a few places in the paper

With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given by
\begin{equation}
    \begin{split}
        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_k) + \mat{H}'_{k,i}\rvec{x}_k) \\
        &= 
        \begin{bmatrix}
            \begin{split}
                &(2\rv{r}_{k,i}^{-1})\rv{x}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_k^2 \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{x}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{x}_k \\
                &\quad+ (2\rv{r}_{k,i}^{-1}s_{x,i}^3) + (2\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i}^2) \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i} \rv{z}'_{k,i})
            \end{split}
            \vspace{5pt}\\
            \begin{split}
                &(2\rv{r}_{k,i}^{-1})\rv{y}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_k^2 \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{y}_k \\
                &\quad+ (2\rv{r}_{k,i}^{-1}s_{y,i}s_{x,i}^2) + (2\rv{r}_{k,i}^{-1}s_{y,i}^3) \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i}\rv{z}'_{k,i})
            \end{split}
        \end{bmatrix}
    \end{split} \label{eqn:hrz_linear_comb}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}\mat{H}'_{k,i} \\
        &=
        \begin{bmatrix}
            \alpha_{11} & \alpha_{12} \\
            \alpha_{21} & \alpha_{22}
        \end{bmatrix}\,,
    \end{split} \label{eqn:hrh_linear_comb}
\end{equation}
with
\begin{align*}
    \alpha_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_k + (4\rv{r}_{k,i}^{-1}s_{x,i}^2) \\
    \begin{split}
        \alpha_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k + (-4\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_k + (-4\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_k \\
        &\qquad+ (4\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i})
    \end{split}\\
    \alpha_{21} &= \alpha_{12} \\
    \alpha_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_k + (4\rv{r}_{k,i}^{-1}s_{y,i}^2)\,.
\end{align*}
The above rearrangements result in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of the weights $\rv{x}_k^3$, $\rv{y}_k^3$, $\rv{x}_k^2\rv{y}_k$, $\rv{x}_k\rv{y}_k^2$, $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k$ and $\rv{y}_k$, which again capture all the required information private to the navigator.

@@

        \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k,\rv{y}_k\rangle$} 
            \State Compute $\mathsf{E}_{0}(\rv{\omega})$ by \eqref{eqn:encode}
            \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ by \eqref{eqn:our_scheme_encrypt}
            \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ to sensors
        \EndFor

>>>>

With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given by
\begin{equation}
    \begin{split}
        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_k) + \mat{H}'_{k,i}\rvec{x}_k) \\
        &= 
        \begin{bmatrix}
            \begin{split}
                &(2\rv{r}_{k,i}^{-1})\rv{x}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_k^2 \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{x}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{x}_k \\
                &\quad+ (2\rv{r}_{k,i}^{-1}s_{x,i}^3) + (2\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i}^2) \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i} \rv{z}'_{k,i})
            \end{split}
            \vspace{5pt}\\
            \begin{split}
                &(2\rv{r}_{k,i}^{-1})\rv{y}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_k^2 \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{y}_k \\
                &\quad+ (2\rv{r}_{k,i}^{-1}s_{y,i}s_{x,i}^2) + (2\rv{r}_{k,i}^{-1}s_{y,i}^3) \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i}\rv{z}'_{k,i})
            \end{split}
        \end{bmatrix}
    \end{split} \label{eqn:hrz_linear_comb}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}\mat{H}'_{k,i} \\
        &=
        \begin{bmatrix}
            \alpha_{11} & \alpha_{12} \\
            \alpha_{21} & \alpha_{22}
        \end{bmatrix}\,,
    \end{split} \label{eqn:hrh_linear_comb}
\end{equation}
with
\begin{align*}
    \alpha_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_k + (4\rv{r}_{k,i}^{-1}s_{x,i}^2) \\
    \begin{split}
        \alpha_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k + (-4\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_k + (-4\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_k \\
        &\qquad+ (4\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i})
    \end{split}\\
    \alpha_{21} &= \alpha_{12} \\
    \alpha_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_k + (4\rv{r}_{k,i}^{-1}s_{y,i}^2)\,.
\end{align*}
The above rearrangements result in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of the weights $\rv{x}_k^3$, $\rv{y}_k^3$, $\rv{x}_k^2\rv{y}_k$, $\rv{x}_k\rv{y}_k^2$, $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k\rv{y}_k$, $\rv{x}_k$ and $\rv{y}_k$, which again capture all the required information private to the navigator.

@@

        \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k\rv{y}_k,\rv{x}_k,\rv{y}_k\rangle$} 
            \State Compute $\mathsf{E}_{0}(\rv{\omega})$ by \eqref{eqn:encode}
            \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ by \eqref{eqn:our_scheme_encrypt}
            \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ to sensors
        \EndFor
